

https://wmbriggs.substack.com/p/the-randomized-in-randomized-controlled?utm_source=profile&utm_medium=reader2
Science Is Not The Answer
The Randomized In Randomized Controlled Trials Is Pure Superstition; Bad Magic
William M Briggs
Jul, 5. 2023
Why You Need To Read This
My dear readers, a complex subject today, presented in the guise of a book review.
/media/urbina/Seagate Expansion Drive/2023-aldaketa_20230525/Desktop/2023_mitoak_20230329/eredu-estatistikoa_20230428/Nancy Cartwright, Jeremy Hardie, Eleonora Montuschi, Matthew Soleiman, Ann C. Thresher - The Tangle of Science_ Reliability Beyond Method, Rigour, and Objectivity-Oxford University Press (2023).epub
https://www.wmbriggs.com/uncertainty-book/

https://www.wmbriggs.com/post/39409/
Massive Over-Certainties In Medicine: Bad Statistics, Bad Experiments
By Briggs on March 16, 2022	

https://www.wmbriggs.com/post/39423/
Curious Notions Of Cause In Science & Statistics
By Briggs on March 17, 2022
Counterfactuals

https://www.wmbriggs.com/post/10601/
Causation And Correlation
By Briggs on December 18, 2013

https://www.wmbriggs.com/post/45670/
The Reason Why Much Science Is Broken: Every Use Of P-Values Is A Logical Fallacy
By Briggs on February 27, 2023

https://www.wmbriggs.com/post/27051/
Stop Using P-values & Parameter-Centric Methods
By Briggs on May 3, 2019
I wrote two papers with about a dozen or two arguments proving my contention that every use of a p-value is fallacious or mistaken.
Here is one: https://www.wmbriggs.com/public/Briggs.Reality.Based.Prob.Stats.pdf
, here is the other: 
https://www.wmbriggs.com/post/26125/
New Paper! Everything Wrong With P-values Under One Roof
By Briggs on January 8, 2019
Here is a link to the PDF.
Briggs, William M., 2019. Everything Wrong with P-Values Under One Roof. In Beyond Traditional Probabilistic Methods in Economics, V Kreinovich, NN Thach, ND Trung, DV Thanh (eds.), pp 22–44. DOI 978-3-030-04200-4_2
/home/urbina/Downloads/Briggs.Reality.Based.Prob.Stats.pdf
/home/urbina/Downloads/Briggs.EverthingWrongWithPvalues.pdf

https://www.wmbriggs.com/post/41539/
Statistics
Canada’s Science Coronadoom Model Discovers Canada’s Science Saved 800 Thousand Lives
By Briggs on August 8, 2022	
An agent-based model is like a computer game where the NPCs are give greater complexity, with parameters galore, all of which require specifying. And all of which describe interactions the modeler decides in advance. Because all models only say what they are told to say.
This is just like we saw last week. This is a model of a model of a model of who knows how many more models used to justify the main model. And no indication whatsoever that the substantial uncertainty of each model in the web of models is carried over into the next model downstream (this is like the multiplying uncertainties example we did before). In short, the entire contraption is hideously over-certain.





https://wherearethenumbers.substack.com/p/climate-change-by-flawed-numbers
Climate change by flawed numbers
The "at least 95% certainty of man-made warming" scam
Norman Fenton
Jul 5, 2023
fallacy of the transposed conditional (or ‘prosecutor fallacy’) 



https://wherearethenumbers.substack.com/p/the-lancet-has-become-a-laughing
Where are the numbers? by Norman Fenton and Martin Neil
The Lancet has become a laughing stock
Norman Fenton
and Martin Neil
Jan 14, 2023
https://wherearethenumbers.substack.com/p/alroy-preis
The curious case of Dr Sharon Alroy-Preis and the claims of safety and effectiveness of the Pfizer vaccine
Norman Fenton
and Martin Neil
Jan 10, 2023



https://wherearethenumbers.substack.com/p/the-dark-horse-podcast-reports-on
Where are the numbers? by Norman Fenton and Martin Neil
The Dark Horse Podcast reports on 'the illusion of vaccine efficacy '
Martin Neil
and Norman Fenton
Jun 25, 2023



https://metatron.substack.com/p/how-to-create-a-deadly-pandemic-in?utm_source=substack&utm_campaign=post_embed&utm_medium=web
Dead Man Talking
Discover more from Dead Man Talking
Dead people don't lie. Empirical analysis of mortality and other data to eke out the truth about COVID.
Over 23,000 subscribers
Continue reading
Sign in
How to create a deadly pandemic in five easy steps
A playbook for dictators and psycho-philanthropists globally.
Joel Smalley
Jun 29, 2023


https://metatron.substack.com/p/the-covid-vaccines-saved-millions
Dead Man Talking
"The COVID Vaccines Saved Millions of Lives"
A test of the hypothesis - and a parable about falling off a ship.
Joel Smalley
Jul 4, 2023

https://metatron.substack.com/p/there-was-no-pandemic
Dead Man Talking
There Was No Pandemic
An essay by Denis Rancourt
Joel Smalley
Jun 28, 2023

https://williamhunterduncan.substack.com/p/there-was-no-covid-19-pandemic?utm_source=substack&utm_campaign=post_embed&utm_medium=web
There Was No Covid-19 Pandemic
Occam's Razor, the biology of viruses, the naked ambition for power and the Philosopher's Stone.
William Hunter Duncan
Dec 31, 2022

https://anamihalceamdphd.substack.com/p/the-truth-about-the-1918-spanish
Dr. Ana’s Newsletter
The TRUTH about the 1918 Spanish Flu Virus and Pandemic
Keeping an open mind about everything you are being told
Ana Maria Mihalcea, MD, PhD
Aug 8, 2022
https://www.conservativewoman.co.uk/why-i-dont-believe-there-ever-was-a-covid-virus/
Why I don’t believe there ever was a Covid virus
By
Dr Mike Yeadon
March 22, 2023

https://metatron.substack.com/p/the-greatest-violation-of-medical
"The Greatest Violation of Medical Ethics in the History of Medicine, Maybe Humanity"
Michael Kowalik
Writes Michael Kowalik’s Newsletter
Feb 25
·edited Feb 25
Liked by Joel Smalley
Any population-level harms vs benefits of vaccines are ethically uninteresting. Even if the vaccine had caused all the alleged health problems, this would not match the harm caused by the precedent of removing the right to free medical consent (for any reason) and the precedent that it is morally permissible to kill an unlucky minority for the alleged benefit of the majority. This is the kind of harm that will affect future generations even if the present vaccine were a placebo, and unless solved now, it opens the door again for crimes against humanity being committed under the guise of healthcare. When corporate personalities like Tucker are ‘outraged’ about medical harms of vaccines, their owners do not want you to see the bigger picture. https://michaelkowalik.substack.com/p/why-vaccine-mandates-are-unethical
https://michaelkowalik.substack.com/p/why-vaccine-mandates-are-unethical
"The sacrosanct, golden rule of pregnancy has been broken." Dr James Thorp - Board Certified Obstetrician-Gynaecologist
Joel Smalley
Feb 24, 2023












________________________________________________________________________


How to make a realistic old rubber stamp?
https://tex.stackexchange.com/questions/96106/how-to-make-a-realistic-old-rubber-stamp


Calligraphic logo in tikz
https://tex.stackexchange.com/questions/47898/calligraphic-logo-in-tikz

Recreating a logo (text around a circle)
https://tex.stackexchange.com/questions/75638/recreating-a-logo-text-around-a-circle
https://tex.stackexchange.com/questions/493500/making-a-logo-with-arabic-text?noredirect=1&lq=1
https://tex.stackexchange.com/questions/96678/toward-a-stamper-package


https://www.togaware.com/linux/survivor/transparent-images.html
We can replace the white background of a JPG image with a transparent background to create a PNG image using convert from imagemagick. The key option is -transparent:


https://itsfoss.com/install-imagemagick-ubuntu/
comprobar si está instalado
convert -version
Version: ImageMagick 6.9.11-60 Q16 x86_64 2021-01-25 https://imagemagick.org
Copyright: (C) 1999-2021 ImageMagick Studio LLC
License: https://imagemagick.org/script/license.php
Features: Cipher DPC Modules OpenMP(4.5) 
Delegates (built-in): bzlib djvu fftw fontconfig freetype heic jbig jng jp2 jpeg lcms lqr ltdl lzma openexr pangocairo png tiff webp wmf x xml zlib
Está
sudo apt install imagemagick


$ convert -transparent white orig.jpg trans.png
$ display trans.png


https://stackoverflow.com/questions/9155377/set-transparent-background-using-imagemagick-and-commandline-prompt
















